---
title: "What is the Temperature?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What is the Temperature?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Tempetell)
```
**Introduction** <br/>
This is a guide to a Weather station package. 
It uses your location to get 20 of the nearest weather stations.
It provides you with a data-frame and a map of the weather stations.
The map has markers for the weather stations with temperature data.


**GPS Function**
Below is the location function which uses a Google API to get the coordinates of the location of the user.
It uses the httr package to post the requests to the google API.
```{r}
gps<- location()
```

**Stations Function** <br/>
Below is the populate list function which takes the coordinates of the user from the location function as its parameters.
This function posts a request to a weather API and returns a data-frame with atleast 20 of the nearest weather stations with temperature and humidity data.
It utilizes the httr package to post the request to the API, and the jsonlite package to translate the content from the API from GeoJSON to human readable format and then creates a dataframe with the information.
```{r}
stations <- PopulateList(gps)
```

**Stations Map** <br/>
Below is the Station map function which takes the weather stations and coordinates from the previous functions as its parameters.
It uses a leaflet package to create a map of the 20 nearest weather stations from the previous functions.
The weather stations are displayed on a OSM base-map with blue markers and display temperature data for each station. (Click on a marker to see the name and the temperature of each station.)
To get the station Map  you call on the StationMap function with the stations and locations as it parameters
```{r}
temptell <- stationMap(stations,gps)
temptell
```

**Disclaimer** <br/>
This package has the following WARNING :
  Found the following file with non-ASCII characters:
    tempetell.R
  Portable packages must use only ASCII characters in their R code,
  except perhaps in comments.
This is because this package is using an API and the API responses or data contain non-ASCII characters.
Those characters are triggering the warning.
